Scalable Extreme Deconvolution

### 2019-09-03 ml4ps_paper/paper.tex
Add plot of RA vs Dec.

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}
\usepackage{color}      % microtypography

@@

\todo{Add a 2D projection of an example solution?}

\begin{table}
  \caption{Total validation and test log-likelihoods along with average training time for the Gaia data subset. Average over 5 runs with standard deviation.}
  \label{results-table}
  \centering
  \begin{tabular}{lccc}
    \toprule
    Method     & Validation     & Test & Training Time (minutes) \\
    \midrule
    Existing EM (\citet{bovyExtremeDeconvolutionInferring2011}) & $-5.191 (\pm 0.0080) \times 10^6$  & - & $101.1 \pm 2.19$    \\
    Minibatch EM & $-5.183 (\pm 0.0005) \times 10^6$    & - & $48.7 \pm 0.39$      \\
    SGD     & $-5.193 (\pm 0.0029) \times 10^6$        & - & $36.0 \pm 0.34$ \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{color}
\usepackage{graphicx}

@@

\begin{table}
  \caption{Average validation and test log-likelihoods with average training time for the Gaia data subset for different numbers of mixture components $K$.  Average over 5 runs with standard deviation.}
  \label{results-table}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    Method     & K &  Validation     & Test & Time (minutes) \\
    \midrule
    Existing EM  & 128 & $-25.95 \pm 0.04$  & - & $101.1 \pm 2.19$    \\
    (\citet{bovyExtremeDeconvolutionInferring2011}) & 256 & $-25.76 \pm 0.02$ & - & $195.3 \pm 4.08$ \\
    \midrule
    Minibatch EM & 128 & $-25.92 \pm 0.01$ & - & $44.5 \pm 1.0$      \\
    & 256 & $-25.83 \pm 0.003$ & - & $51.6 \pm 3.0$ \\
    \midrule
    SGD  & 128  & $-25.94 \pm 0.01$ & - & $34.0 \pm 0.83$ \\
    & 256 &$-25.84 \pm 0.01$ & - & $36.6 \pm 1.3$ \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{figure}
  \centering
  \includegraphics{density.pdf}
  \caption{Density plot showing a 2-D projection of 100000 samples drawn from a model with $K=256$ and fitted with the minibatch EM method.
  The plot shows the estimated density of star positions on the sky, and has correctly recovered the structure of the Milky Way.}
\end{figure}
